A Low-cost Natural Interaction System based on a Camera Hand-Gestures Recognizer

### 2011-02-04 paper.tex
Thomas Last night remarks

\frontmatter          % for the preliminaries
\pagestyle{headings}  % switches on printing of running heads
\mainmatter              % start of the contributions
%
\title{A Low-cost Natural Interaction based on a Camera Hand-Gestures Recognizer}
\author{Mohamed-Ikbel Boulabiar\inst{1} \and Thomas Burger\inst{2}
Franck Poirier\inst{3} \and Gilles Coppin\inst{1}}
%
\institute{LAB-STICC, Telecom-Bretagne, France,\\
\email{boulabiar@gmail.com, gilles.coppin@telecom-bretagne.eu},
\and
LAB-STICC, University of Bretagne-Sud, France
\email{thomas.burger@univ-ubs.fr}
\and
VALORIA, University of Bretagne-Sud, France
\email{franck.poirier@univ-ubs.fr}
}

@@

\begin{abstract}
The search for new simplified interaction techniques is always treated as a
manner to advance the communication with interactive devices.
In this paper, we present our work to generate interactive TVs modules capable
of recognizing human gestures through the PS3Eye low-cost camera.
We recognize gestures by the tracking of human skin blobs and analyzing the 
corresponding movements to control a TV in an ubiquitous computing environment.
We also present a new free gestures icons library created to allow easy
representation and diagramming.
%after an analysis of TV's Talk-shows.

@@

\section{Introduction}
HCI research focuses more attention than before on enhancing the user experience
regarding human-display interaction in order to interact more naturally without
the need of clicking on buttons and touching screens. However, in everyday life
interaction with home devices having embedded computational power, such as
interactive TVs, one does not make benefit of these new interaction paradigms yet.

We present in this paper an approach that could allow the detection and the
interpretation of gestures of a TV spectator from a simple and low cost camera. 
RevTV is the name of the French project for adding new interaction techniques
to TVs to allow the inclusion of the telespectator.
%The final objective of this study is to control the animations of an avatar
%that should be inserted within a TV show beside the presenter or actor [RevTV].
Its major scenario which we rely on, corresponds to educational games where a
pupil controls his/her avatar in a program led by a ``real'' TV animator.
This kind of scenarios needs to be able to manage commands interaction
like pointing, selecting and moving as well as natural gesture animation.

@@

This semantics can be divided into two parts:
\begin{description}
 \item[Animation Gestures] used to animate a virtual avatar.
 \item[Command Gestures] used to launch a specific predefined action.
\end{description}

@@

\subsection{Gestures taxonomies}
By looking at the possible gestures human can generate \cite{Gesturecraft}, we
get a huge amount of possibilities which depend on the context and on the type.
%So, there is a need for a taxonomy.
%Many possible taxonomies exist according to the technical or analytical aspects:
%In order to describe and analyse each gesture, we can rely on the following aspects:
\ignore{\begin{description}
 \item[Gesture Creation Space:] We use this criteria to distinguish between gestures made in the 2D or 3D space.
 \item[Number of used strokes:] We use this criteria to distinguish between gestures constructed by only one path and between those using many paths, so the recognition needs to wait for all strokes before the recognition
 \item[Gesture context:] We use this criteria to distinguish gesture based on the specific use of it, gestures for disabled people, gestures in talk-shows, gestures in meetings.
\end{description}}
%Gesture and Thoughts, page 18
According to McNail \cite{gestureThought}, it is possible and useful to
distinguish between these gestures and a possbile taxonomy can provide us these
types:
\begin{description}
 \item[Gesticulation] is a motion that embodies a meaning reliable to the
accompanying speech. It is made chiefly with the arms and hands but is not
restricted to these body parts.
 \item[Speech-linked gestures] are parts of sentences themselves, the gesture
completes the sentence structure.
 \item[Emblems] are conventionalized signs, such as thumbs-up or the ring (first
finger and thumb tips touching, other fingers extended) for ``OK.''
 \item[Pantomime] is dumb show, a gesture or sequence of gestures conveying a
narrative line, with a story to tell, produced without speech.
\end{description}

In our work, we focalize on emblems commands and gesticulations.
%We have chosen to analyze gesticulations as they are the most frequent.
%, and project them on the technical taxonomies.
%And we have also made our own extraction from Talk-Shows.
%Nous avons choisi celle-ci, car elle correspond aux besoins que nous avons identifier dans les scenarios d'utilisation de la télé interactive

@@

In order to identify relevant gestures we have analyzed some talk-shows in order
to extract most frequent gestures being performed.
According to our scenario of use in the context of Interacrive TV.
%and defining a benchmark scenario.
%We have tried to target the following kinds of gestures in a first step.

@@

Fig.\ref{handg} shows our supported gestures. We provide a movement mode
used to select the 4 directions, then a multitouch nthen a command mode, then a hand fingers recognition,
and, finally, a cursor movement mode.
%\pagebreak 
We have selected 4 basic gestures modes to be supported in our system as a first step.
Then to be extended depending on the context fulfilling the requirements
of our scenario.

@@

\subsection{Color Transformations}
The video processing is based on several modules.
First, a basic but adaptive skin color segmentation of a large interval of human skin varieties is performed \cite{skinColorSeg}.
We also use a histogram equalisation technique to better enlarge the colors to all the space available.
Then we transform the color space from BGR, which come from the camera to YCrCb,
as it’s the most adapted one to skin segmentation
Moreover, the corresponding transformation is linear \cite{skinColorSeg}.

@@

\subsection{Input Filtering}
During this step, a 5x5 opening morphological kernel \cite{morphologicalAnalysis} is applied to smooth the results,
this is necessary to clean the image from isolated pixels and holes inside skin
zones.

>>>>

\frontmatter          % for the preliminaries
\pagestyle{headings}  % switches on printing of running heads
\mainmatter              % start of the contributions
%
\title{A Low-cost Natural Interaction System based on a Camera Hand-Gestures Recognizer}
\author{Mohamed-Ikbel Boulabiar\inst{1} \and Thomas Burger\inst{2}
Franck Poirier\inst{3} \and Gilles Coppin\inst{1}}
%
\institute{LAB-STICC, Telecom-Bretagne, France,\\
\email{boulabiar@gmail.com, gilles.coppin@telecom-bretagne.eu},
\and
LAB-STICC, University of Bretagne-Sud, France
\email{thomas.burger@univ-ubs.fr}
\and
VALORIA, University of Bretagne-Sud, France
\email{franck.poirier@univ-ubs.fr}
}

@@

\begin{abstract}
The search for new simplified interaction techniques is 
mainly motiviated by the improvements of 
the communication with interactive devices.
In this paper, we present an interactive TVs module capable
of recognizing human gestures through the PS3Eye low-cost camera.
We recognize gestures by the tracking of human skin blobs and analyzing the 
corresponding movements. It provides means to control a TV in an ubiquitous computing environment.
We also present a new free gestures icons library created to allow easy
representation and diagramming.
%after an analysis of TV's Talk-shows.

@@

\section{Introduction}
HCI research focuses more attention than before on enhancing the user
experience regarding human-display interaction in order to interact
more naturally without the need of clicking on buttons and touching screens.
However, in everyday life, interaction with home devices having
embedded computational power, such as interactive TVs,
one does not make benefit from these new interaction paradigms yet.

We present in this paper an approach that could allow the detection and the
interpretation of gestures of a TV spectator from a simple and low cost camera. 
RevTV is the name of the French project for adding new interaction techniques
to TVs to allow the inclusion of the telespectator.
%Pourquoi as-tu enlevé cette phrase (ligne suivante) ? Cela me semblait une bonne introduction à la présentation du projet.

%The final objective of this study is to control the animations of an avatar that should be inserted within a TV show beside the presenter or actor [RevTV].
One major scenario that we rely on, corresponds to some educational game where a pupil
controls his/her avatar which interact in a forecast program led by a ``real'' TV animator.
During such kind of scenarios, commands interaction
like pointing, selecting and moving, as well as natural gesture animation, are required.

\ignore{
%The final objective of this study is to control the animations of an avatar
%that should be inserted within a TV show beside the presenter or actor [RevTV].
Its major scenario which we rely on, corresponds to educational games where a
pupil controls his/her avatar in a program led by a ``real'' TV animator.
This kind of scenarios needs to be able to manage commands interaction
like pointing, selecting and moving as well as natural gesture animation.
}
% Il faut rajouter une description du projet Rev-TV

@@

This semantics can be divided into two parts:
\begin{description}
 \item[Animation Gestures] used to animate a virtual avatar.
 \item[Command Gestures] used to launch a specific predefined action.
\end{description}
%%%
% toute cette partie me semble incompréhensible... (entre la debut de la section 2 et la début de la 2.1)
% Je veux bien t'aider à la rédiger, mais je ne comprends pas vraiment ce que tu veux dire... 
% Quel est ton message ?

@@

\subsection{Gestures taxonomies}
A rapid look the possible gestures human can perform \cite{Gesturecraft}, lead to the conclusion that the amount of possibilities is tremoundous. Nonetheless, the gestures can be classified according to various criteria. Here, we consider a taxonomy based on the context of the gestures as well as on their types:
%%%%%%%
%By looking at the possible gestures human can generate \cite{Gesturecraft}, we
%get a huge amount of possibilities which depend on the context and on the type.

%So, there is a need for a taxonomy.
%Many possible taxonomies exist according to the technical or analytical aspects:
%In order to describe and analyse each gesture, we can rely on the following aspects:
\ignore{\begin{description}
 \item[Gesture Creation Space:] We use this criteria to distinguish between gestures made in the 2D or 3D space.
 \item[Number of used strokes:] We use this criteria to distinguish between gestures constructed by only one path and between those using many paths, so the recognition needs to wait for all strokes before the recognition
 \item[Gesture context:] We use this criteria to distinguish gesture based on the specific use of it, gestures for disabled people, gestures in talk-shows, gestures in meetings.
\end{description}}
%Gesture and Thoughts, page 18
According to McNail \cite{gestureThought}, it is possible and useful to
distinguish between these gestures and a possbile taxonomy can provide us these
types:
\begin{description}
 \item[Gesticulation] is a motion that embodies a meaning reliable to the
accompanying speech. It is made chiefly with the arms and hands but is not
restricted to these body parts.
 \item[Speech-linked gestures] are parts of sentences themselves, the gesture
completes the sentence structure.
 \item[Emblems] are conventionalized signs, such as thumbs-up or the ring (first
finger and thumb tips touching, other fingers extended) for ``OK.''
 \item[Pantomime] is dumb show, a gesture or sequence of gestures conveying a
narrative line, with a story to tell, produced without speech.
\end{description}

In our work, we focalize on emblems commands and gesticulations, as both of them are of prime importance for the scenario under consideration.
%We have chosen to analyze gesticulations as they are the most frequent.
%, and project them on the technical taxonomies.
%And we have also made our own extraction from Talk-Shows.
%Nous avons choisi celle-ci, car elle correspond aux besoins que nous avons identifier dans les scenarios d'utilisation de la télé interactive

@@

% Il faut rédiger complétement cette partie... C'est pas compréhensible, et il n'y a pas de verbe dans la seconde phrase.
In order to identify relevant gestures we have analyzed some talk-shows in order
to extract most frequent gestures being performed.
According to our scenario of use in the context of Interacrive TV.
%and defining a benchmark scenario.
%We have tried to target the following kinds of gestures in a first step.

@@

Figure\ref{handg} shows our supported gestures. We provide a movement mode
used to select the 4 directions, then a multitouch, then a command mode, then a hand fingers recognition,
and, finally, a cursor movement mode.
%\pagebreak 
We have selected 4 basic gestures modes to be supported in our system as a first step.
Then to be extended depending on the context fulfilling the requirements
of our scenario.

@@

\subsection{Color Transformations} %%%%%%%%%%%%%%%%%%%
The video processing is based on several modules, such as illustrated in Fig ... .
First, a basic but adaptive skin color segmentation of a large interval of human skin varieties is performed \cite{skinColorSeg}.
We also use a histogram equalisation technique to better enlarge the colors to all the space available.
Then we transform the color space from BGR, which come from the camera to YCrCb,
as it is the most adapted one to skin segmentation
Moreover, the corresponding transformation is linear \cite{skinColorSeg}, which helps computation time saving.

@@

\subsection{Input Filtering}
During this step, a 5x5 opening morphological kernel \cite{morphologicalAnalysis} is applied to smooth the results.
Practically, it cleans the image from isolated pixels and holes inside skin
zones.
